Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
experiments: polished

The presented reduction algorithms have been implemented in a tool called
\telatko. It uses the Spot library~\cite{duret.16.atva2} for automata parsing
and manipulation, and the Z3 Theorem Prover~\cite{demoura.08.tacas} to solve
the satisfiability of QBF formulas. Moreover, in the experimental evaluation
we use several tools from the Spot library, i.e. \texttt{genltl},
\texttt{ltlfilt}, \texttt{ltl2tgba}, \texttt{autcross} and \texttt{autfilt},
to generate, simplify and translate LTL formulas and to compare and simplify
automata. \telatko is implemented in Python.

@@

@@

Looking at Figure~\ref{fig:quantile}, we ascertain that for every set, the
reduction of most automata takes under a second.

>>>>

The presented reduction algorithms have been implemented in a tool called
\telatko. It uses the Spot library~\cite{duret.16.atva2} for automata parsing
and manipulation, and the Z3 Theorem Prover~\cite{demoura.08.tacas} to solve
the satisfiability of QBF formulas. \telatko is implemented in Python.

@@

We have used multiple other helper tools in the experimental evaluation.
Alongside \texttt{genltl}, we have used \texttt{ltlfilt} to simplify the
formulas and to remove duplicates, and \texttt{autcross} to compare automata and
measure the running times.

@@

Figure~\ref{fig:quantile} presents the time spent by reducing the individual
automata sets. The chart shows a pleasing finding that for every set, most
automata are reduced in under a second and the high cummulative running times
are caused by few complicated automata.
